a and generators

### 2022-09-15 documentos/proofdiagonalization.tex
comentarios
Make Sure You Are Square With Your God Before Trying To Merge This

binary indices instead of a single quaternary, i.e. $\alpha\to j +2 k$. For

@@

Back to the Eq. \ref{Choi_a1}), let us apply the index relabeling $k\to j+
k (\text{mod} 2)$, then the Choi matrix reads

@@

For the sake of convenience in the demonstration of several useful properties
of the PCE channels, 
we shall reorder the eigenvalues, to write 
\begin{equation}
\lambda =  \frac12 \sa \tau
\end{equation}
with 
\begin{equation}
\sa=\left(
\begin{array}{cccc}
1 &1 &1   &1   \\
 1 & 1  & -1&-1   \\
1  & -1  & 1 & -1\\
1&-1&-1&1  
\label{a_appendix}
\end{array}
\right),
\end{equation}\janote{esta matriz ya está en el cuerpo principal del artículo. Sugiero quitar de acá.}
instead of $H\otimes H$. This can be done due to the fact
that both matrices ($\sa$ and $H \otimes H$) are equivalent up to a permutation of rows. 
In other words this operation corresponds to a reordering of the eigenvalues.

% }}}
\subsection{$N$ qubits} % {{{
To work out the $N$ qubit case, we again rely on binary indices. In this case, we replace 
$N$ dimensional vector $\valpha$ with a pair of $N$ dimensional vector binary
indices $\vec j$ and $\vec k$ so that 
each entry $\alpha_i$ of $\valpha$ is identified with the pair $j_i$ and $k_i$ as in the 
single qubit case of the previous subsection. Then, all the steps leading to 
\eref{eq:lambda:is:tau:appendix} can be redone.

The tensor product of Pauli matrices, in vector form,  will be denoted by 
$\kket{\sigma_{\vec{k}\vec{l} }}$.
% \begin{equation}
% \bbrakket{\sigma_{\vec{k}\vec{l} }}{\sigma_{\vec{k}'\vec{l}'}} = 2^N \delta_{\vec{k}\vec{k}'}\delta_{\vec{l}\vec{l}'}.
% \end{equation}
With this in mind, a $N$-qubit Pauli map can be written as 
% 
% 
% Analogously to the previous case, we can define an arbitrary Pauli map acting on $N$ qubits density matrices in terms of the tensor products of vectorized Pauli matrices
\begin{equation}
\hat{\mathcal{E}}_N = 
  \frac{1}{2^N}\sum_{\vec{l}\vec{m}} \tau_{\vec{l}\vec{m}} \ddyada{\sigma_{\vec{l}\vec{m} }}. 
\end{equation}
The generalization of Eqs.~(\ref{CompToPau}) and (\ref{PauToComp}) read 
\begin{align}
\kket{\sigma_{\vec{k}\vec{l} }}  & = 
   \sum_{\vec{j}} (-1)^{\vec{j}\cdot\vec{k}} \ket{\vec{j}}\ket{\vec{j}+ \vec{l}(\text{mod}2)},\\
%
 \ket{\vec{l}}\ket{\vec{l}+ \vec{n}(\text{mod}2)} & = 
   \frac{1}{2^N}\sum_{\vec{m}} (-1)^{\vec{m}\cdot\vec{l}}\kket{\sigma_{\vec{m}\vec{n} }}.
\end{align}
% \afnote{Cambiar los $\mu$ y $\nu$ por indices latinos.}

@@

the map, $\hat{\mathcal{E}}_N $ in the $N$-qubits computational basis as

@@

$\hat{\mathcal{E}}_N$ to obtain the associated Choi matrix, 

>>>>

binary indices instead of a single quaternary, i.e., $\alpha\to j +2 k$. For

@@

Returning to the Eq. \ref{Choi_a1}), let us apply the index relabeling $k\to j+
k (\text{mod} 2)$; then the Choi matrix reads

@@

For the sake of convenience in the demonstration of several useful properties
of the PCE channels, 
we shall reorder the eigenvalues, to write 
\begin{equation}
\lambda =  \frac12 \sa \tau
\end{equation}
with $a$ the matrix shown in~\eref{eq:1} 
instead of $H\otimes H$. This can be done due to the fact
that both matrices ($\sa$ and $H \otimes H$) are equivalent up to a permutation of rows. 
In other words this operation corresponds to a reordering of the eigenvalues.

% }}}
\subsection{$N$ qubits} % {{{
To work out the $N$-qubit case, we again rely on binary indices. In this case, we replace 
$N$-dimensional vector $\valpha$ with a pair of $N$-dimensional vector binary
indices $\vec j$ and $\vec k$ so that 
each entry $\alpha_i$ of $\valpha$ is identified with the pair $j_i$ and $k_i$ as in the 
single-qubit case of the previous subsection. Then, all the steps leading to 
\eref{eq:lambda:is:tau:appendix} can be redone.

The tensor product of Pauli matrices, in vector form,  will be denoted by 
$\kket{\sigma_{\vec{k}\vec{l} }}$.
% \begin{equation}
% \bbrakket{\sigma_{\vec{k}\vec{l} }}{\sigma_{\vec{k}'\vec{l}'}} = 2^N \delta_{\vec{k}\vec{k}'}\delta_{\vec{l}\vec{l}'}.
% \end{equation}
With this in mind, a $N$-qubit Pauli map can be written as 
% 
% 
% Analogously to the previous case, we can define an arbitrary Pauli map acting on $N$ qubits density matrices in terms of the tensor products of vectorized Pauli matrices
\begin{equation}
\hat{\mathcal{E}}_N = 
  \frac{1}{2^N}\sum_{\vec{l}\vec{m}} \tau_{\vec{l}\vec{m}} \ddyada{\sigma_{\vec{l}\vec{m} }}. 
\end{equation}
The generalizations of Eqs.~(\ref{CompToPau}) and (\ref{PauToComp}) read 
\begin{align}
\kket{\sigma_{\vec{k}\vec{l} }}  & = 
   \sum_{\vec{j}} (-1)^{\vec{j}\cdot\vec{k}} \ket{\vec{j}}\ket{\vec{j}+ \vec{l}(\text{mod}2)},\\
%
 \ket{\vec{l}}\ket{\vec{l}+ \vec{n}(\text{mod}2)} & = 
   \frac{1}{2^N}\sum_{\vec{m}} (-1)^{\vec{m}\cdot\vec{l}}\kket{\sigma_{\vec{m}\vec{n} }}.
\end{align}
% \afnote{Cambiar los $\mu$ y $\nu$ por indices latinos.}

@@

the map, $\hat{\mathcal{E}}_N $ in the $N$-qubit computational basis as

@@

$\hat{\mathcal{E}}_N$ to obtain the associated Choi matrix, and

### 2022-09-15 documentos/vector_space.tex
Make Sure You Are Square With Your God Before Trying To Merge This

Let us start by recalling that the problem of determining complete positivity
of a PCE map can be recast as determining which coefficients $\tau_\valpha$ 
are mapped via $\san$
% \begin{equation}
% \san\vec\tau=2^N\vec p
% \label{eq:condition}
% \end{equation}
to positive eigenvalues $\lambda_\valpha$, as in \eref{eq:lambda:is:A:tau}. 
% . In components, this would read 
% \begin{equation}
% % \left(
% \sum_\vbeta
% \san_{\valpha\vbeta} \,
% % \right)
% \tau_{\vec \beta}=2^Np_{\vec\alpha}
% \label{eq:A:tau:is:p}
% \end{equation}
% where
% $\san_{\vec\alpha\vec\beta} =\sa_{\alpha_1\beta_1}\cdot\ldots\cdot
% \sa_{\alpha_N\beta_N}$. 
Using the fact that $a^{-1}=a/4$, so 
% (so $A = A^{-1}/2^N$) 
\begin{equation}
A^{-1} = \frac{1}{4^N} A,
\end{equation}
we can directly invert \eref{eq:lambda:is:A:tau} to obtain 
\begin{equation}
% \tau_{\vec \alpha}= \san_{\vec\alpha\vec\beta} \, p_\vbeta,
% \tau = 
% \san \lambda =2^N \tau
\sum_\vbeta \san_{\valpha \vbeta} \lambda_\vbeta =2^N \tau_\valpha
\label{eq:tau:is:A:p}
\end{equation}
which will serve as a starting point for our analysis. 
This is a remarkable equation, as it provides a method to diagonalize the
Choi matrix of any Pauli diagonal map.

Other two simple but crucial observations are the following. 
For valid quantum channels it holds 
% \begin{equation}
% % \sum_{
% \end{equation}
% $\sum_{\valpha \in \Omega} \lambda_\valpha=0$ implies that 
% $\lambda_\valpha=0$ for all $\valpha$ in an arbitrary subset of 
% multi-indices $\Omega$, 
\begin{equation}
\sum_{\valpha \in \Omega} \lambda_\valpha=0 
\quad \implies 
\quad 
\lambda_\valpha=0, \, \forall \valpha \in \Omega
\label{eq:lambda:is:zero}
\end{equation}
for an arbitrary subset of multi-indices $\Omega$, 
as each member of the sum is greater than or equal to zero, 
due to complete positivity of the underlying channel. 
Finally, setting $\valpha =0$ in \eref{eq:tau:is:A:p}, and taking into 
account the normalization condition that $\tau_{\vec 0}=1$, we obtain
\begin{equation}
\sum_\valpha \lambda_\valpha = 2^N,
\label{eq:sum:alpha:is:2N}
\end{equation}
since, $A_{\vec 0, \vbeta}=1$ for all $\vbeta$. \par
% }}}
% Conexion de los indices para llegar al grupo de Klein {{{
Now we need a definition: to each multi-index $\vec\alpha$ we associate a \textit{set}
of multi-indices $\Phi(\vec\alpha)$ as follows
\begin{equation}
\Phi(\vec\alpha)=\left\{
\vec\beta:\san_{\vec\alpha\vec\beta}=1
\right\}
% =\left\{ \vec\beta: \sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
% =1
% \right\}
\label{eq:8}
\end{equation}
% If we now assume that $\tau_{\vec\alpha}=1$, it follows from subtracting 
If we now assume that $\tau_{\vec\alpha}=1$, and calculate the difference between
\eref{eq:sum:alpha:is:2N} and
$\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}\lambda_{\vec\beta}=2^N$
(which follows from \eref{eq:tau:is:A:p} and $\tau_{\vec\alpha}=1$), one obtains
% \begin{subequations}
% \begin{eqnarray}
% \sum_{\vec\beta}p_{\vec\beta}&=&1
% \label{eq:9a}\\
% \sum_{\vec\beta}\san_{\vec\alpha\vec\beta}p_{\vec\beta}&=&\tau_{\vec\alpha}=1
% \end{eqnarray}
% \label{eq:9}
% \end{subequations}
% that for all $\vec\beta\notin\Phi(\vec\alpha)$
\begin{eqnarray}
\lambda_{\vec\beta}=0,\quad \forall \vec\beta\notin\Phi(\vec\alpha).
\label{eq:condition:lambda:zero:Phi}
\end{eqnarray}
Thus, if $\tau_{\vec\alpha}=1$, then $\tau_{\vec\gamma}$
and $\tau_{\vec{\gamma^\prime}}$ are equal if
% , for all $\vec\beta\in\Phi(\vec\alpha)$.
\begin{equation}
\san_{\vbeta\vec\gamma}=\san_{\vbeta\vec{\gamma^\prime}}, \quad
\forall \vec\beta\in\Phi(\vec\alpha).
\label{eq:coneccion:dos:indices:A}
\end{equation}
This follows from restricting the sum \eref{eq:tau:is:A:p}
to the $\lambda_\vbeta \ne 0$, given in \eref{eq:condition:lambda:zero:Phi}. 
Condition (\ref{eq:coneccion:dos:indices:A}) therefore connects three
multi-indices, $\valpha$,
$\vec\gamma$ and $\vec{\gamma^\prime}$.
When such a connection exists, $\tau_{\vec\alpha}=1$ implies
$\tau_{\vec\gamma}=\tau_{\vec{\gamma^\prime}}$.

Let us now work out the nature of the aforementioned connection.  For arbitrary
$k$ we define a vector $\vbeta_k$ such that $\vbeta_k\in\Phi(\vec\alpha)$ as
follows: $\vbeta_k$ is zero everywhere except
for the $k$'th coordinate, which takes a value $\beta$ such that  $\sa_{\alpha_k\beta}=1$. Since 
$\sa_{\alpha 0}=1$ for any $\alpha$, this particular choice of $\vbeta$
indeed belongs to  $\Phi(\vec\alpha)$, so that if \eref{eq:coneccion:dos:indices:A} holds for 
all $\vbeta\in\Phi(\vec\alpha)$, it must hold for that particular $\vbeta_k$, which leads to:
% 
% Let us now work out the nature of the aforementioned connection.  Let the
% components of  $\vbeta$ be such that $\beta_l = \beta \delta_{lk}$ for a
% particular particle index $k$, with $\beta$ such that $\sa_{\alpha_k\beta}=1$.
% Since $\sa_{\alpha 0}=1$ for any $\alpha$, this particular choice of $\vbeta$
% belongs to  $\Phi(\vec\alpha)$, so that \eref{eq:coneccion:dos:indices:A}
% indeed holds. However, for such a choice
% of $\vbeta$ the above relation reduces
% to 
\begin{equation}
\sa_{\beta\gamma_k}=\sa_{\beta\gamma_k^\prime}
\label{eq:14}
\end{equation}
for all $\beta$ such that $\sa_{{\alpha_k}\beta}=1$.  One can verify, by
working out the different cases, that \eref{eq:14} is equivalently expressed as 
\begin{equation}
\gamma_k^\prime=\alpha_k\oplus{}\gamma_k
\label{eq:oplus}
\end{equation}
where the $\oplus{}$ denotes the operation of the Klein group; see Table
\ref{tab:1} for a detailed description. 
\par
% }}}
% Espacio vectorial {{{

It will be useful to think of the multi-index $\valpha$ as an element of 
a vector space. To do so, we notice that any group with the property that
$\alpha \oplus \alpha =0$ is indeed a vector space under the two-element field
$\{0,1\}$.
We notice that the Klein group described in Table \ref{tab:1} is actually isomorphic
to the two dimensional vector space over the field of two elements $\{0,1\}$.
Then, we build the complete vector space,
with the same field, and defining $\valpha \oplus \vbeta = (\alpha_1 \oplus
\beta_1,\cdots, \alpha_N \oplus \beta_N)$
\footnote{
We can further unravel the vector space, by identifying each index
$\alpha \in \{0,1,2,3\}$ with its binary notation [e.g. identify $2$ with $(1,0)$]
such that to each multindex  $\valpha$ there corresponds a binary string of 
length $2N$. In fact, our sum $\oplus$ would correspond to addition modulo 2 of 
each of the $2N$ components. 
}. 
We can indeed restate \eref{eq:oplus}, and say that for quantum channels, 
if $\tau_{\vec\alpha}=1$, then
$\tau_{\vec\gamma}=\tau_{\vec\alpha\oplus{}\vec\gamma}$.
For example, in \fref{fig:two:qubit:examples}(c) the indices that 
correspond to preserved components are 
$\valpha^{(0)} = (0,0)$, 
$\valpha^{(1)} = (0,2)$, 
$\valpha^{(2)} = (1,0)$, 
$\valpha^{(3)} = (2,2)$, and
$\valpha^{(4)} = (3,2)$. However, 
$\valpha^{(1)} + \valpha^{(2)} = (1,2)$, which is not preserved, and thus this 
diagram does not correspond to a quantum channel.  From this view 
we can derive several interesting observations that will be presented in 
the rest of the section.

\begin{table} % {{{
\begin{center}
\begin{tabular}{| c | c c c c |}
\hline
$\oplus{}$ & 0 & 1& 2 & 3\\
\hline
0 & 0 & 1 & 2 & 3\\
1 & 1 & 0 & 3 & 2\\
2 & 2 & 3 & 0 & 1 \\
3 &3 & 2 & 1 & 0\\
\hline
\end{tabular}
\caption{Definition of the $\oplus{}$ operation, see \eref{eq:14}. Note that
the operation is an abelian group, in fact it corresponds to the 
Klein group, where the neutral element is $0$. This is the reason for choosing
an additive notation for the operation defined in (\ref{eq:14}). }
\label{tab:1}
\end{center}
\end{table} % }}}

From this readily follows an amusing property: the set of all multi-indices
$\vec\gamma$ for which $\tau_{\vec\gamma}=1$, is closed under binary
vector addition, in other words, it forms a vector subspace of the set
of all multi-indices.
A moment's consideration will further show that the above reasoning can be
inverted, that is, that if we set all $\tau_{\vec\gamma}$ equal to one
whenever the $\vec\gamma$ belongs to a given vector subspace of the set of
all indices, then $\tau$ indeed has an image
which has
only positive components. 
In other words, there is a one-to-one correspondence between 
a quantum channel, and a vector subspace of the aforementioned space. 
\par

% }}}
% Generacion de soluciones {{{
With this information, we present a procedure to generate all solutions: we start out
from the solution having $\tau_{\vec0}=1$, with everything else $0$. We may
then successively switch $\tau_{\vec\alpha}$'s
% \janote{agregué el subíndice $\vec\alpha$} 
to $1$ for various values of $\valpha$,
taking care immediately to set equal to one the components of $\tau$
% \janote{puse la $\tau$ como vector y hay otro antes}
that
correspond to values of $\vbeta$ generated by the previously switched values of
$\valpha$ via the operation $\oplus$. Doing so, in an ordered way, allows one
to generate
all PCE quantum channels with a given set of preserved components, without the need
of exploring the exponentially large space of all PCE maps.  \par 
% }}}}

@@

Examples of diagrams for several 2-qubit PCE quantum channels: (a) the totally
depolarizing channel, (b) a PCE channel that preserves four components, the
normalization component, one local component of qubit 2 and two correlations between the 

@@

(c), (d) and (e) show the three generators $\mcG_{(1,0)}$, $\mcG_{(3,2)}$ and

@@

 % }}}
% Cuantos canales conservan $2^K$ componentes? {{{
It is natural to ask how many PCE quantum channels exist that preserve  $2^K$ components. One
can calculate such number, $\sss_{N,K}$, by examining the number of different
independent subsets of vectors that spawn a given vector subspace. In appendix 
\ref{app:contar} we show that 
\begin{equation}
\sss_{N,K}=\prod_{m=0}^{K-1} \frac{2^{2N-m}-1}{2^{K-m}-1}.
\label{eq:conteo:main}
\end{equation}
%An elementary test is $N=3$ and $K=2,3$: 
%\begin{eqnarray}
%\sss_{3,2}&=&\frac{(2^6-1)(2^5-1)}{(2^2-1)(2^1-1)}=\frac{63\cdot31}{3}=651,\\
%\sss_{3,3}&=&\frac{(2^6-1)(2^5-1)(2^4-1)}{(2^3-1)(2^2-1)(2^1-1)}=\frac{63\cdot31\cdot15}{7\cdot3}=1395,
%\end{eqnarray}
%which are indeed the values found numerically. 
From the above expression, it is easy to see the symmetry relation
\begin{equation}\label{eq:conteo:simmetry}
\sss_{N,K}=\sss_{N,2N-K}
\end{equation}
which suggest a relation  between individual channels that
preserve $K$ and $2N-K$ Pauli components that for the time being
has escaped our efforts to identify. 
\par % }}}

>>>>

Let us start by recalling that the problem of determining complete positivity
of a PCE map can be recast as determining which coefficients $\tau_\valpha$ 
are mapped via $\san$
% \begin{equation}
% \san\vec\tau=2^N\vec p
% \label{eq:condition}
% \end{equation}
to positive eigenvalues $\lambda_\valpha$, as in \eref{eq:lambda:is:A:tau}. 
% . In components, this would read 
% \begin{equation}
% % \left(
% \sum_\vbeta
% \san_{\valpha\vbeta} \,
% % \right)
% \tau_{\vec \beta}=2^Np_{\vec\alpha}
% \label{eq:A:tau:is:p}
% \end{equation}
% where
% $\san_{\vec\alpha\vec\beta} =\sa_{\alpha_1\beta_1}\cdot\ldots\cdot
% \sa_{\alpha_N\beta_N}$. 
Using the fact that $a^{-1}=a/4$, and so 
% (so $A = A^{-1}/2^N$) 
\begin{equation}
A^{-1} = \frac{1}{4^N} A,
\end{equation}
we can directly invert \eref{eq:lambda:is:A:tau} to obtain 
\begin{equation}
% \tau_{\vec \alpha}= \san_{\vec\alpha\vec\beta} \, p_\vbeta,
% \tau = 
% \san \lambda =2^N \tau
\sum_\vbeta \san_{\valpha \vbeta} \lambda_\vbeta =2^N \tau_\valpha
\label{eq:tau:is:A:p}
\end{equation}
which will serve as a starting point for our analysis. 
This is a remarkable equation, as it provides a method to diagonalize the
Choi matrix of any Pauli diagonal map.

Two other simple but crucial observations are the following. 
For valid quantum channels it holds that 
% \begin{equation}
% % \sum_{
% \end{equation}
% $\sum_{\valpha \in \Omega} \lambda_\valpha=0$ implies that 
% $\lambda_\valpha=0$ for all $\valpha$ in an arbitrary subset of 
% multi-indices $\Omega$, 
\begin{equation}
\sum_{\valpha \in \Omega} \lambda_\valpha=0 
\quad \implies 
\quad 
\lambda_\valpha=0, \, \forall \valpha \in \Omega
\label{eq:lambda:is:zero}
\end{equation}
for an arbitrary subset of multi-indices $\Omega$, 
as each member of the sum is greater than or equal to zero, 
due to complete positivity of the underlying channel. 
Finally, setting $\valpha =0$ in \eref{eq:tau:is:A:p}, and taking into 
account the normalization condition that $\tau_{\vec 0}=1$, we obtain
\begin{equation}
\sum_\valpha \lambda_\valpha = 2^N,
\label{eq:sum:alpha:is:2N}
\end{equation}
since, $A_{\vec 0, \vbeta}=1$ for all $\vbeta$. \par
% }}}
% Conexion de los indices para llegar al grupo de Klein {{{
Now we need a definition: to each multi-index $\vec\alpha$ we associate a \textit{set}
of multi-indices $\Phi(\vec\alpha)$ as follows
\begin{equation}
\Phi(\vec\alpha)=\left\{
\vec\beta:\san_{\vec\alpha\vec\beta}=1
\right\}
% =\left\{ \vec\beta: \sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
% =1
% \right\}
\label{eq:8}
\end{equation}
% If we now assume that $\tau_{\vec\alpha}=1$, it follows from subtracting 
If we now assume that $\tau_{\vec\alpha}=1$, and calculate the difference between
\eref{eq:sum:alpha:is:2N} and
$\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}\lambda_{\vec\beta}=2^N$
(which follows from \eref{eq:tau:is:A:p} and $\tau_{\vec\alpha}=1$), one obtains
% \begin{subequations}
% \begin{eqnarray}
% \sum_{\vec\beta}p_{\vec\beta}&=&1
% \label{eq:9a}\\
% \sum_{\vec\beta}\san_{\vec\alpha\vec\beta}p_{\vec\beta}&=&\tau_{\vec\alpha}=1
% \end{eqnarray}
% \label{eq:9}
% \end{subequations}
% that for all $\vec\beta\notin\Phi(\vec\alpha)$
\begin{eqnarray}
\lambda_{\vec\beta}=0,\quad \forall \vec\beta\notin\Phi(\vec\alpha).
\label{eq:condition:lambda:zero:Phi}
\end{eqnarray}
Thus, if $\tau_{\vec\alpha}=1$, then $\tau_{\vec\gamma}$
and $\tau_{\vec{\gamma^\prime}}$ are equal if
% , for all $\vec\beta\in\Phi(\vec\alpha)$.
\begin{equation}
\san_{\vbeta\vec\gamma}=\san_{\vbeta\vec{\gamma^\prime}}, \quad
\forall \vec\beta\in\Phi(\vec\alpha).
\label{eq:coneccion:dos:indices:A}
\end{equation}
This follows from restricting the sum \eref{eq:tau:is:A:p}
to $\lambda_\vbeta \ne 0$, given in \eref{eq:condition:lambda:zero:Phi}. 
Condition (\ref{eq:coneccion:dos:indices:A}) therefore connects three
multi-indices, $\valpha$,
$\vec\gamma$ and $\vec{\gamma^\prime}$.
When such a connection exists, $\tau_{\vec\alpha}=1$ implies
$\tau_{\vec\gamma}=\tau_{\vec{\gamma^\prime}}$.

Let us now work out the nature of the aforementioned connection.  For arbitrary
$k$ we define a vector $\vbeta_k$ such that $\vbeta_k\in\Phi(\vec\alpha)$ as
follows: $\vbeta_k$ is zero everywhere except
for the $k$'th coordinate, which takes a value $\beta$ such that  $\sa_{\alpha_k\beta}=1$. Since 
$\sa_{\alpha 0}=1$ for any $\alpha$, this particular choice of $\vbeta$
indeed belongs to  $\Phi(\vec\alpha)$, so that if \eref{eq:coneccion:dos:indices:A} holds for 
all $\vbeta\in\Phi(\vec\alpha)$, it must hold for that particular $\vbeta_k$, which leads to
% 
% Let us now work out the nature of the aforementioned connection.  Let the
% components of  $\vbeta$ be such that $\beta_l = \beta \delta_{lk}$ for a
% particular particle index $k$, with $\beta$ such that $\sa_{\alpha_k\beta}=1$.
% Since $\sa_{\alpha 0}=1$ for any $\alpha$, this particular choice of $\vbeta$
% belongs to  $\Phi(\vec\alpha)$, so that \eref{eq:coneccion:dos:indices:A}
% indeed holds. However, for such a choice
% of $\vbeta$ the above relation reduces
% to 
\begin{equation}
\sa_{\beta\gamma_k}=\sa_{\beta\gamma_k^\prime}
\label{eq:14}
\end{equation}
for all $\beta$ such that $\sa_{{\alpha_k}\beta}=1$.  One can verify, by
working out the different cases, that \eref{eq:14} is equivalently expressed as 
\begin{equation}
\gamma_k^\prime=\alpha_k\oplus{}\gamma_k
\label{eq:oplus}
\end{equation}
where $\oplus{}$ denotes the operation of the Klein group; see Table
\ref{tab:1} for a detailed description. 
\par
% }}}
% Espacio vectorial {{{

It will be useful to think of the multi-index $\valpha$ as an element of 
a vector space. To do so, we notice that any group with the property that
$\alpha \oplus \alpha =0$ is indeed a vector space under the two-element field
$\{0,1\}$.
We notice that the Klein group described in Table \ref{tab:1} is actually isomorphic
to the two-dimensional vector space over the field of two elements $\{0,1\}$.
Then, we build the complete vector space,
with the same field, and defining $\valpha \oplus \vbeta = (\alpha_1 \oplus
\beta_1,\cdots, \alpha_N \oplus \beta_N)$
\footnote{
We can further unravel the vector space, by identifying each index
$\alpha \in \{0,1,2,3\}$ with its binary notation [e.g. identify $2$ with $(1,0)$]
such that to each multindex  $\valpha$ there corresponds a binary string of 
length $2N$. In fact, our sum $\oplus$ would correspond to addition modulo 2 of 
each of the $2N$ components. 
}. 
We can indeed restate \eref{eq:oplus} and say that, for quantum channels, 
if $\tau_{\vec\alpha}=1$, then
$\tau_{\vec\gamma}=\tau_{\vec\alpha\oplus{}\vec\gamma}$.
For example, in \fref{fig:two:qubit:examples}(c) the indices that 
correspond to preserved components are 
$\valpha^{(0)} = (0,0)$, 
$\valpha^{(1)} = (0,2)$, 
$\valpha^{(2)} = (1,0)$, 
$\valpha^{(3)} = (2,2)$, and
$\valpha^{(4)} = (3,2)$. However, 
$\valpha^{(1)} + \valpha^{(2)} = (1,2)$, which is not preserved, and thus this 
diagram does not correspond to a quantum channel.  From this view 
we can derive several interesting observations that will be presented in 
the rest of the section.

\begin{table} % {{{
\begin{center}
\begin{tabular}{| c | c c c c |}
\hline
$\oplus{}$ & 0 & 1& 2 & 3\\
\hline
0 & 0 & 1 & 2 & 3\\
1 & 1 & 0 & 3 & 2\\
2 & 2 & 3 & 0 & 1 \\
3 &3 & 2 & 1 & 0\\
\hline
\end{tabular}
\caption{Definition of the $\oplus{}$ operation, see \eref{eq:14}. Note that
the operation is an Abelian group; in fact it corresponds to the 
Klein group, where the neutral element is zero. This is the reason for choosing
an additive notation for the operation defined in (\ref{eq:14}). }
\label{tab:1}
\end{center}
\end{table} % }}}

From this readily follows an amusing property: the set of all multi-indices
$\vec\gamma$ for which $\tau_{\vec\gamma}=1$ is closed under binary
vector addition; in other words, it forms a vector subspace of the set
of all multi-indices.
A moment's consideration will further show that the above reasoning can be
inverted; that is, if we set all $\tau_{\vec\gamma}$ equal to $1$
whenever $\vec\gamma$ belongs to a given vector subspace of the set of
all indices, then $\tau$ indeed has an image
which has
only positive components. 
In other words, there is a one-to-one correspondence between 
a quantum channel, and a vector subspace of the aforementioned space. 
\par

% }}}
% Generacion de soluciones {{{
With this information, we present a procedure to generate all solutions: we start out
from the solution having $\tau_{\vec0}=1$, with everything else zero. We may
then successively switch $\tau_{\vec\alpha}$'s
% \janote{agregué el subíndice $\vec\alpha$} 
to one for various values of $\valpha$,
taking care immediately to set equal to one the components of $\tau$
% \janote{puse la $\tau$ como vector y hay otro antes}
that
correspond to values of $\vbeta$ generated by the previously switched values of
$\valpha$ via the operation $\oplus$. Doing so, in an ordered way, allows one
to generate
all PCE quantum channels with a given set of preserved components, without the need
of exploring the exponentially large space of all PCE maps.  \par 
% }}}}

@@

Examples of diagrams for several two-qubit PCE quantum channels: (a) the totally
depolarizing channel and (b) a PCE channel that preserves four components---the
normalization component, one local component of qubit 2, and two correlations between the 

@@

(c), (d), and (e) show the three generators $\mcG_{(1,0)}$, $\mcG_{(3,2)}$, and

@@

 % }}}
% Cuantos canales conservan $2^K$ componentes? {{{
It is natural to ask how many PCE quantum channels exist that preserve  $2^K$ components. One
can calculate such number, $\sss_{N,K}$, by examining the number of different
independent subsets of vectors that spawn a given vector subspace. In appendix 
\ref{app:contar} we show that 
\begin{equation}
\sss_{N,K}=\prod_{m=0}^{K-1} \frac{2^{2N-m}-1}{2^{K-m}-1}.
\label{eq:conteo:main}
\end{equation}
%An elementary test is $N=3$ and $K=2,3$: 
%\begin{eqnarray}
%\sss_{3,2}&=&\frac{(2^6-1)(2^5-1)}{(2^2-1)(2^1-1)}=\frac{63\cdot31}{3}=651,\\
%\sss_{3,3}&=&\frac{(2^6-1)(2^5-1)(2^4-1)}{(2^3-1)(2^2-1)(2^1-1)}=\frac{63\cdot31\cdot15}{7\cdot3}=1395,
%\end{eqnarray}
%which are indeed the values found numerically. 
From the above expression, it is easy to see the symmetry relation
\begin{equation}\label{eq:conteo:simmetry}
\sss_{N,K}=\sss_{N,2N-K}
\end{equation}
which suggests a relation  between individual channels that
preserve $K$ and $2N-K$ Pauli components that for the time being
has escaped our efforts to identify. 
\par % }}}
